---
title: "Statiscal Inference Course Project Part2"
author: "Andres Felipe Lagos Ruiz"
date: "9/18/2020"
output:
  pdf_document: default
  html_document: default
---

## Abstact

this is the second part of the project Statistical Inference. In this second part, it is making basics inference of the data set Tooth grown.  

This data set is the response of odontoblasts in each of 10 guinea pigs at each of three dose levels of vitamin C(0.5,1 and 2 mg).  

### load the libraries

 ```{r,echo=T}
 library(ggplot2)
 #load the library of the data set
 library(datasets)
 data(ToothGrowth)
 #see the data set summary
 summary(ToothGrowth)
 str(ToothGrowth)
 ```
### Provide a basic summary of the data

 ```{r,echo=T,fig.height=3}
#see the difference case between dose levels and delivery methods
table(ToothGrowth$dose,ToothGrowth$supp)
#Visualizate the improve of tooth growth for supplement type
g<-ggplot(aes(x=supp, y=len), data=ToothGrowth) + geom_boxplot(aes(fill=supp))
g+labs(title = "Tooth growth vs Supplement type")
# see the graphics of dose levels vs delivery method
g<-ggplot(aes(x=dose, y=len,group=dose), data=ToothGrowth) + geom_boxplot(aes(fill=dose))
g+labs(title = "difference type of doses")
```
### Use confidence intervlas and hypothesis to compare tooth growth by support and dose
 ```{r,echo=T}
# peform the difference of support type by group
t.test(len~supp,data=ToothGrowth)
```
taking this results it is possible to say that the difference supplement type have not effect on the tooth length

 ```{r,echo=T}
 # making the analises of the three type of dose
 TG0.5<-ToothGrowth[ToothGrowth$dose==0.5,]
 TG1<-ToothGrowth[ToothGrowth$dose==1,]
 TG2<-ToothGrowth[ToothGrowth$dose==2,]
 #Make the analises for dose =0.5
 t.test(len~supp, data = TG0.5)
 #Make the analises for dose =1
 t.test(len~supp, data = TG1)
 #Make the analises for dose =2
 t.test(len~supp, data = TG2)
 ```
### Conclucions

It is possible to say that when you improved the doses the null hypothesis of tooth growth can be reject